A Decision Procedure for (Co)datatypes in SMT Solvers

### 2016-02-09 sister/sister.tex
fixed

The decision procedure for (co)datatypes is useful both for proving (via
negation, in the refutational style) and for model finding
\cite{ge-de-moura-2009,reynolds-et-al-2013}.
It is in fact vital for finite model finding,
because the acyclicity and uniqueness rules are necessary for solution
soundness, without which the generated models would often be
spurious. For example, given the constraints
\begin{align*}
\const{zeros} & = \const{SCons}(0,\:\const{zeros})
& \const{sconst}~n & = \const{SCons}(n,\:\const{sconst}~n)
\end{align*}
the conjecture
$\const{zeros} = \const{sconst}~0$
would be ``refuted'' by a spurious countermodel that interprets
\const{zero} and $\const{sconst}~0$ by two distinct
values $\MU s.\; \const{SCons}(0, s)$,
violating uniqueness.

>>>>

The decision procedure for (co)datatypes is useful both for proving (via
negation, in the refutational style) and for model finding
\cite{ge-de-moura-2009,reynolds-et-al-2013}.
It is in fact vital for finite model finding,
because the acyclicity and uniqueness rules are necessary for solution
soundness, without which the generated models would often be
spurious. For example, given the constraints
\begin{align*}
\const{zeros} & \teq \const{SCons}(0,\:\const{zeros})
& \const{repeat}(n) & \teq \const{SCons}(n,\:\const{repeat}(n))
\end{align*}
the conjecture
$\const{zeros} = \const{repeat}(0)$
would be ``refuted'' by a spurious countermodel that interprets
\const{zero} and $\const{repeat}(0)$ by two distinct
values $\MU s.\; \const{SCons}(0, s)$,
violating uniqueness.
